\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-30 paper.qmd
Update binning data section

Points are allocated to the bin they fall into based on the nearest centroid. In situations where a point is equidistant from multiple centroids, tie-breaking rules are applied. If multiple centroids are in the same row, the point is assigned to the leftmost centroid. If multiple centroids are in different rows, the point is assigned to the bottom centroid.

$\{ i \in H_h, h = 1, \dots, b, \text{ and } i = 1, \dots, n\}$

Let $u : \mathbb{R}^{n\times k} \rightarrow \mathbb{R}^{m\times k}$ be the function that maps a point in \kD{} space to it's bin centroid ($C^{(k)}$). This is the model points in \kD{} space.

When $k = 2$, one of the representations of a bin is the hexagonal centroid (@fig-NLDR-scurve (c)). Also, it could be the mean of the data points within each hexagon.

@@

The last step is to lift the \kD{} model into \pD{} by computing \pD{} vectors that represent bin centroids. We use the \pD{} mean of the points in $H_h$ to map the centroid $C_{h}^{(k)} = (c_{h1}, c_{h2}, \dots, c_{hk})$ to a point in \pD{}. Let the \pD{} mean be

>>>>

<!-- Points are allocated to the bin they fall into based on the nearest centroid. In situations where a point is equidistant from multiple centroids, tie-breaking rules are applied. If multiple centroids are in the same row, the point is assigned to the leftmost centroid. If multiple centroids are in different rows, the point is assigned to the bottom centroid. -->

<!-- $\{ i \in H_h, h = 1, \dots, b, \text{ and } i = 1, \dots, n\}$ -->

We define the function $u: \mathbb{R}^{n\times 2} \rightarrow \mathbb{R}^{m\times 2}$, which generates the model by assigning the points to bin centroids.

For the $i^{th}$ point, $u(i) = \arg\min_{j = 1, \dots, b} \sqrt{(y_{i1} - C^{(2)}_{j1})^2 + (y_{i2} - C^{(2)}_{j2})^2}$, and falls in $H_h = \{i| u(i) = h\}$.

When $k = 2$, the hexagonal bin centroid is one representation of a bin (@fig-NLDR-scurve (c)). Additionally, it can be the mean of the points within each hexagon.

@@

The last step is to lift the \kD{} model into \pD{} by computing \pD{} vectors that represent bin centroids. We use the \pD{} mean of the points in $H_h$ to map the centroid $C_{h}^{(2)} = (c_{h1}, c_{h2})$ to a point in \pD{}. Let the \pD{} mean be

### 2024-05-30 paper.tex
Update binning data section

Points are allocated to the bin they fall into based on the nearest
centroid. In situations where a point is equidistant from multiple
centroids, tie-breaking rules are applied. If multiple centroids are in
the same row, the point is assigned to the leftmost centroid. If
multiple centroids are in different rows, the point is assigned to the
bottom centroid.

\(\{ i \in H_h, h = 1, \dots, b, \text{ and } i = 1, \dots, n\}\)

Let \(u : \mathbb{R}^{n\times k} \rightarrow \mathbb{R}^{m\times k}\) be
the function that maps a point in \kD{} space to it's bin centroid
(\(C^{(k)}\)). This is the model points in \kD{} space.

When \(k = 2\), one of the representations of a bin is the hexagonal
centroid (Figure~\ref{fig-NLDR-scurve} (c)). Also, it could be the mean
of the data points within each hexagon.

@@

The last step is to lift the \kD{} model into \pD{} by computing \pD{}
vectors that represent bin centroids. We use the \pD{} mean of the
points in \(H_h\) to map the centroid
\(C_{h}^{(k)} = (c_{h1}, c_{h2}, \dots, c_{hk})\) to a point in \pD{}.
Let the \pD{} mean be

>>>>

We define the function
\(u: \mathbb{R}^{n\times 2} \rightarrow \mathbb{R}^{m\times 2}\), which
generates the model by assigning the points to bin centroids.

For the \(i^{th}\) point,
\(u(i) = \arg\min_{j = 1, \dots, b} \sqrt{(y_{i1} - C^{(2)}_{j1})^2 + (y_{i2} - C^{(2)}_{j2})^2}\),
and falls in \(H_h = \{i| u(i) = h\}\).

When \(k = 2\), the hexagonal bin centroid is one representation of a
bin (Figure~\ref{fig-NLDR-scurve} (c)). Additionally, it can be the mean
of the points within each hexagon.

@@

The last step is to lift the \kD{} model into \pD{} by computing \pD{}
vectors that represent bin centroids. We use the \pD{} mean of the
points in \(H_h\) to map the centroid \(C_{h}^{(2)} = (c_{h1}, c_{h2})\)
to a point in \pD{}. Let the \pD{} mean be
